\paperTitle

### 2014-01-31 doc/icml2014/directed.tex
Convered TODO to \todo

[TODO: need to say we're going to do this for the infinite data case,
and then study bounds]

[TODO: try to be consistent: either use latent or hidden]

@@

  Let $x_v$ be an observed variable with parents $P$ and children $C$.
  Consider the following transformation.
  Replace $x_v$ with a new hidden variable \hp\ with the same
  parents $\Pa(x_v)$ and children $\text{Ch}(x_v) \union \{x_{v_1}, x_{v_2}, x_{v_3}\}$,
  where $x_{v_1},x_{v_2},x_{v_3}$ are three copies of $x$
  (\figureref{reduction}). 
  The domain of $\hp$ is the same as $x$,
    and $\mOpp{v}{\textrm{new}} = I$.\footnote{Though we have assumed that all hidden variables share the
      same domain, $[k]$, our work generalizes to hidden domains of
      arbitrary sizes.
      [TODO: add qualifier]
      %provided \assumptionref{full-rank-plus} holds.
      }

@@

[TODO: somewhere give examples that are not in our class, preferably the simplest one, cite Sontag]

@@

% DONE: move here because not central to story
\paragraph{Remark.} We note that \propertyref{bottleneck} can be relaxed if some cliques
  share parameters.
In the directed grid model, we can identify the conditional moments $O$ from just
  $x^a_1, x^b_1$ and $x^a_2$.
  Therefore, we do not require that $h_2, h_3$ or $h_4$
  be bottlenecks, and can omit the observations $x^b_2, x^b_3$ and $x^b_4$.
  [TODO: make this a footnote if running out of space]
% PL: don't understand this comment
%In this case, we only require that the hidden variables in distinct
  %cliques share parameters.

@@

\LearnMarginals~ combines two consistent algorithms, \TensorFactorize and
\LearnClique, [TODO: too much space after LearnClique] and is thus consistent itself.
[TODO: did they prove this; if so just say "they show", not "we can show"]
Using results from
  \citet{anandkumar12moments,anandkumar13tensor} we can show that
  learning $\mOpp{v_1}{i}$ for the bottleneck $h_i$ with views $x_{v_1},
  x_{v_2}, x_{v_3}$ has the following sample complexity,
  [TODO: define hat O]
  [TODO: max subscript is misaligned]
\begin{align*}
  \|\mOpphat{v_1}{i} - \mOpp{v_1}{i}\|^2_F &= \frac{1}{\sqrt{n}} O\left( \frac{k {\pi\oft{i}}_{\max}^2}{\sigma_k(M_{v_1,v_2})^5} \right). 
\end{align*}

[TODO: call MOM squared]
We next describe the asymptotic variance for \LearnClique when using the
  method of moments.
\begin{lemma}(Asymptotic variance of $Z_\sC$)
  \label{lem:mom-variance}  
  The asymptotic variance of $Z_\sC$ is:
  \begin{align*}
    \Sigma^{\mom} &= \mOppAlli \Sigma_\sV \mOppAllit,
  \end{align*}
  where $\pinv{\mOppAll} \eqdef \pinv{\mOpp{v_1}{i_1}} \otimes
  \cdots \otimes \pinv{\mOpp{v_m}{i_m}}$, a $d^m \times k^m$ matrix, and 
\begin{align*}
  \Sigma_\sV &= \text{\rm diag}(M_\sV) - M_\sV M_\sV^\top,
\end{align*}
  is the asymptotic variance of the observations $M_\sV$.
\end{lemma}
\begin{proof}
We have for each clique,
\begin{align*}
  Z_{\sC} &= \mO_\sV(\mOppi{v_1}{i_1},\cdots,\mOppi{v_m}{i_m}) \\
\end{align*}

>>>>

\todo{need to say we're going to do this for the infinite data case,
and then study bounds}

\todo{try to be consistent: either use latent or hidden}

@@

  Let $x_v$ be an observed variable with parents $P$ and children $C$.
  Consider the following transformation.
  Replace $x_v$ with a new hidden variable \hp\ with the same
  parents $\Pa(x_v)$ and children $\text{Ch}(x_v) \union \{x_{v_1}, x_{v_2}, x_{v_3}\}$,
  where $x_{v_1},x_{v_2},x_{v_3}$ are three copies of $x$
  (\figureref{reduction}). 
  The domain of $\hp$ is the same as $x$,
    and $\mOpp{v}{\textrm{new}} = I$.\footnote{Though we have assumed that all hidden variables share the
      same domain, $[k]$, our work generalizes to hidden domains of
      arbitrary sizes.
      \todo{add qualifier}
      %provided \assumptionref{full-rank-plus} holds.
      }

@@

\todo{somewhere give examples that are not in our class, preferably the simplest one, cite Sontag}

@@

% DONE: move here because not central to story
\paragraph{Remark.} We note that \propertyref{bottleneck} can be relaxed if some cliques
  share parameters.
In the directed grid model, we can identify the conditional moments $O$ from just
  $x^a_1, x^b_1$ and $x^a_2$.
  Therefore, we do not require that $h_2, h_3$ or $h_4$
  be bottlenecks, and can omit the observations $x^b_2, x^b_3$ and $x^b_4$.
  \todo{make this a footnote if running out of space}
% PL: don't understand this comment
%In this case, we only require that the hidden variables in distinct
  %cliques share parameters.

@@

\LearnMarginals~ combines two consistent algorithms, \TensorFactorize and
\LearnClique, \todo{too much space after LearnClique} and is thus consistent itself.
\todo{did they prove this; if so just say "they show", not "we can show"}
Using results from
  \citet{anandkumar12moments,anandkumar13tensor} we can show that
  learning $\mOpp{v_1}{i}$ for the bottleneck $h_i$ with views $x_{v_1},
  x_{v_2}, x_{v_3}$ has the following sample complexity,
  \todo{define hat O}
  \todo{max subscript is misaligned}
\begin{align*}
  \|\mOpphat{v_1}{i} - \mOpp{v_1}{i}\|^2_F &= \frac{1}{\sqrt{n}} O\left( \frac{k {\pi\oft{i}}_{\max}^2}{\sigma_k(M_{v_1,v_2})^5} \right). 
\end{align*}

\todo{call MOM squared}
We next describe the asymptotic variance for \LearnClique when using the
  method of moments.
\begin{lemma}(Asymptotic variance of $Z_\sC$)
  \label{lem:mom-variance}  
  The asymptotic variance of $Z_\sC$ is:
  \begin{align*}
    \Sigma^{\mom} &= \mOppAlli \Sigma_\sV \mOppAllit,
  \end{align*}
  where $\pinv{\mOppAll} \eqdef \pinv{\mOpp{v_1}{i_1}} \otimes
  \cdots \otimes \pinv{\mOpp{v_m}{i_m}}$, a $d^m \times k^m$ matrix, and 
\begin{align*}
  \Sigma_\sV &= \text{\rm diag}(M_\sV) - M_\sV M_\sV^\top,
\end{align*}
  is the asymptotic variance of the observations $M_\sV$.
\end{lemma}
\begin{proof}
We have for each clique,
\begin{align*}
  Z_{\sC} &= \mO_\sV(\mOppi{v_1}{i_1},\cdots,\mOppi{v_m}{i_m}) \\
\end{align*}

### 2014-01-31 doc/icml2014/intro.tex
Convered TODO to \todo

% 1. Latent variable models are good.
Latent-variable graphical models provide compact representations of data
and have been employed across many fields [TODO: find a much better/broader set of citations]
\cite{quattoni04crf,beaumont2004bayesian,haghighi06prototype}.
% 2. Learning them is hard.
However, learning these models remains a difficult problem due to the
non-convexity of the negative log-likelihood.  Local methods such as Expectation Maximization (EM)
are the norm, but are susceptible to local optima.

% 3. People have approached unsupervised learning with the MoM magic sauce, but the sauce is limited.
Recently, unsupervised learning techniques based on the spectral method of moments
have offered a refreshing and promising perspective on
this learning problem
\citep{hsu09spectral,anandkumar11tree,anandkumar12moments,anandkumar12lda,hsu12identifiability,balle11transducer,balle12automata}.
[TODO: make sure we are citing the right people]
These methods exploit the linear algebraic properties of the model to
factorize the moments into parameters, providing strong theoretical guarantees.
However, these methods apply to a limited set of models, and are thus
not as broadly applicable as EM.

\begin{figure}[t]
  \label{fig:approach}
  \centering
  \subimport{figures/}{approach.tikz}
  \caption{[TODO: need three steps: tensor factorization, optimize composite likelihood, recover model parameters; Overview of approach}
\end{figure}

@@

%Our approach also applies to undirected log-linear latent variable
  %models, where we use the recovered marginals to make the learning
  %problem convex (\sectionref{undirected}).
Finally, our approach gracefully extends to more general model families
  in which we are unable to recover the marginal distributions for all
  hidden cliques; in such scenarios, we use posterior regularization to constrain
  EM.  We show that empirically, using such constraints alleviates local
  optima issues.

>>>>

% 1. Latent variable models are good.
Latent-variable graphical models provide compact representations of data
and have been employed across many fields \todo{find a much better/broader set of citations}
\cite{quattoni04crf,beaumont2004bayesian,haghighi06prototype}.
% 2. Learning them is hard.
However, learning these models remains a difficult problem due to the
non-convexity of the negative log-likelihood.  Local methods such as Expectation Maximization (EM)
are the norm, but are susceptible to local optima.

% 3. People have approached unsupervised learning with the MoM magic sauce, but the sauce is limited.
Recently, unsupervised learning techniques based on the spectral method of moments
have offered a refreshing and promising perspective on
this learning problem
\citep{hsu09spectral,anandkumar11tree,anandkumar12moments,anandkumar12lda,hsu12identifiability,balle11transducer,balle12automata}.
\todo{make sure we are citing the right people}
These methods exploit the linear algebraic properties of the model to
factorize the moments into parameters, providing strong theoretical guarantees.
However, these methods apply to a limited set of models, and are thus
not as broadly applicable as EM.

\begin{figure}[t]
  \label{fig:approach}
  \centering
  \subimport{figures/}{approach.tikz}
  \caption{\todo{need three steps: tensor factorization, optimize composite likelihood, recover model parameters;} Overview of approach}
\end{figure}

@@

%Our approach also applies to undirected log-linear latent variable
  %models, where we use the recovered marginals to make the learning
  %problem convex (\sectionref{undirected}).
Finally, our approach gracefully extends to more general model families
  in which we are unable to recover the marginal distributions for all
  hidden cliques; in such scenarios, we use posterior regularization to constrain
  EM.  
\todo{Is this possible?:  We show that empirically, using such constraints alleviates local
optima issues.}
